Death by Dropdown? Engineer Insightful Shiny Apps with Behavioral Science

### 2025-09-07 conference-materials/2025_posit-conf/draft.qmd
Restructure Posit Conf files and enhance telemetry analysis
- Moved R scripts into a dedicated `R/` subdirectory for better organization.
- Refactored `2_bidux.R` to improve readability and switch from `%>%` to native `|>` piping.
- Generated a new telemetry heatmap script (`telemetry_heatmap.R`) to visualize filter usage patterns.
- Added annotated ggplot2-based heatmaps for user interaction insights.
- Updated `renv.lock` with new dependencies.

# Define the destination and goals
interpret_stage <- bid_interpret(
  central_question = "Which markets are driving performance, and where are we lagging?",
  data_story = list(
    hook = "Q4 revenue hit record high, but satisfaction dipped",
    context = "After aggressive marketing across all regions",
    tension = "West region satisfaction fell 10 points",
    resolution = "Focus retention efforts on underperforming regions"
  ),
  user_personas = list(
    list(
      name = "Product Managers",
      goals = "Monitor weekly KPIs",
      technical_level = "Moderate"
    ),
    list(
      name = "Executives",
      goals = "Review quarterly trends",
      technical_level = "Basic"
    )
  )
)
```

>>>>

# Define the destination and goals
interpret_stage <- bid_interpret(
  central_question = "Which markets are driving performance, and where are we lagging?",
  data_story = list(
    hook = "Q4 revenue hit record high, but satisfaction dipped",
    context = "After aggressive marketing across all regions",
    tension = "West region satisfaction fell 10 points",
    resolution = "Focus retention efforts on underperforming regions"
  ),
  user_personas = list(
    list(
      name = "Product Managers",
      goals = "Monitor weekly KPIs",
      pain_points = "Too many filters to find important insights",
      technical_level = "Moderate"
    ),
    list(
      name = "Executives",
      goals = "Review quarterly trends",
      pain_points = "Overwhelmed by data, need clear takeaways",
      technical_level = "Basic"
    )
  )
)

summary(interpret_stage)
```
